Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2012-02-03 ms.tex
Updated figure 4 and 5 captions

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f6.eps}}
\end{center}
\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM
particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits ($0.2^{\circ}$
aperture) presented in this work.}
\label{fig:dm}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f6.eps}}
\end{center}
\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ from VERITAS observations
of the Coma cluster as a function of the DM particle mass $m_{\chi}$ derived from the VERITAS
gamma-ray flux upper limits ($0.2^{\circ}$ aperture) presented in this work.}
\label{fig:dm}
\end{figure*}
